
# Intro to Python

Python is a popular programming language that was created by Guido van Rossum and released in 1991. 

Python is supported by multiple libraries that support data science tasks:

- NumPy for numerical computing with multidimensional arrays
- pandas for data manipulation and analysis with data frames
- Matplotlib for data visualization

The main difference between Python and R is that Python is a general-purpose programming language, while R is a statistical programming language. This means that Python is good at multiple things and can do most things, whereas R is very good at statistical analysis, but not as good at other things as Python.

When you want to document your code, you can use Jupyter Notebooks. Jupyter Notebooks are an open source web application for easily sharing documents that contain your live Python code, equations, visualizations and data science explanations. 

Python is particularly suited for large scale machine learning.


## Learning Objectives

```{r, fig.align='center', echo = FALSE, fig.alt= "Major point!! example image"}
ottrpal::include_slide("https://docs.google.com/presentation/d/1k8uC1rqnGTSbKjBsWvKYgiUUxO1q_VhJCwZQHJNWozA/edit#slide=id.g29054a882fd_0_52")
```

## Python Syntax for R Users

Source: https://rstudio.github.io/reticulate/articles/python_primer.html

Most important difference in syntax is 0-based indexing for Python and 1-based indexing for R. This means that in R, indexing starts with 1 and in Python, indexing starts with 0. Coming from R, this means you have to subtract your "R indexes" by 1 to get the correct index in Python.

Other major differences in Python:

### Whitespace

Important in Python. In R, expressions are grouped into a code block with `{}`. In Python, expressions are grouped by indentation level. 

For example, in R, an if statement looks like:

```{r}
x <- 1

if (x > 0) {
    print("x is positive")
} else {
    print("x is negative")
}
```

In Python, the equivalent if statement looks like:

```{python}
x = 1

if x > 0:
    print("x is positive")
else:
    print("x is negative")
```


### Data Structures


#### Lists


### Tuples


### Dictionaries


### Sets 

### Iteration with for loops

### Comprehensions

### Functions

### Classes


### Importing modules

### Integers and Floats


### Learning More

https://docs.Python.org/3/

https://docs.Python.org/3/library/index.html


